Constructing the transition graphs of interacting hysterons

### 2022-06-28 Paper_draft.tex
Reworked introduction to candidate graphs section to reflect structure change

\section{Model}

@@

\subsection{Ordering of switching fields}

@@

A significant disadvantage of numerical sampling is that it is not conclusive, as it is always possible that a region in parameter space leading to a certain transition graph is missed. Here we aim to establish a tool that can conclusively find all possible graphs for a given number of hysterons $N$.\\
Fortunately, it is not necessary to sample all of parameter space. The reason for this is that the transition graph for a given system does not depend on the absolute values of the switching fields $U_i^{+,-}(S)$, but only on the order of the switching fields. In principle, one could find all possible transition graphs for a given number of hysterons $N$ by evaluating all permutations of the order of the switching fields.\\
In practice, however, it is impractical to find the possible transition graphs by evaluating all possible orderings. This is because the transition graph only depends on a partial order of the switching fields, not on the total order, so that the number of permutations vastly outweighs the number of possible graphs. For example, for the interacting two-hysteron system, there are eight switching fields, giving $8! = 40320$ permutations, and for $N=3$ the number of permutations is $24! \approx 6\times 10^{23}$.\\
Instead of evaluating all permutations of the total order of the switching fields, we find it more useful to take a reverse approach by starting from the topology. We first construct a number of candidate graphs, which describe the behaviour of a hysteron system in a well-defined way but are not necessarily realizable. We then check whether each graph is realizable by evaluating whether there is a region in the parameter space of switching fields corresponding to the graph.\\
The region in parameter space associated with each graph is bounded by a set of linear inequalities that the switching fields must obey, which we refer to as the design inequalities. We generate the design inequalities systematically by combining the conditions on each individual transition. We describe how the design inequalities are found in the Supplemental Information. If the solution space of a graph's design inequalities is not empty, then the graph is realizable. Thus, one can find the possible graphs for $N$ hysterons by first generating the candidate graphs, then checking whether each graph's design inequalities have a solution.\\
In addition to being an efficient method for conclusively finding the possible graphs, the method of candidate graphs also allows us to consider rational design of graphs. We can use the candidate graph method to directly consider the possibility of the interesting behaviours that have been observed previously, such as multiperiodic cycles and long transients, for a  given number of hysterons.\
We here establish our method for finding the transition graphs that are possible for coupled hysterons. We first discuss in section \ref{ssec:candidate_graphs} how one can generate a list of candidate graphs that includes all possible graphs for a given number of hysterons $N$. Next, in section \ref{ssec:realizability}, we explain how to evaluate whether or not a graph is realizable by checking whether its underlying design inequalities have a solution. Finally, we improve on the candidate graph method by introducing the concept of base graphs. 

>>>>

\section{Model}\label{sec:model}

@@

\subsection{Ordering of switching fields}\label{ssec:ordering}

@@

A significant disadvantage of numerical sampling is that it is not conclusive, as it is always possible that a region in parameter space leading to a certain transition graph is missed. Here we aim to establish a tool that can conclusively find all possible graphs for a given number of hysterons $N$. We base our method on the design inequalities, as introduced in Section \ref{ssec:ordering} and elaborated on in the Supplemental Information. We use the design inequalities to argue that the transitions that make up a graph, whether they are single flips or avalanches, can only be constructed out of a set collection of elementary steps. We use our method to construct a list of candidate graphs, then filter out the realizable graphs by explicitly checking the solution space of the design inequalities.\\
